Electric polarizability as the fundamental variable in the dielectric properties of two-dimensional materials

### 2018-12-16 paper.tex
Add HSE datasheet into manuscript and SI

\begin{table}[H]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & &  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption{In-plane ($r_{0}^{\parallel}$) and out-of-plane
    ($r_{0}^{\perp}$) radii of the polarizability ellipsoid of
    selected 2D materials calculated from first principles
    simulations. $r_{0}^{\parallel}$ is in general much larger than
    $r_{0}^{\perp}$, which accounts for the highly anisotropic
    dielectric nature of 2D materials.}
  \label{tbl:radii}  
  \begin{tabular}{lcc}
    \hline
    Material & $r_{0}^{\parallel} = \alpha_{\mathrm{2D}}^{\parallel}/2\varepsilon_{0}$ (\AA{}) &  $r_{0}^{\perp} = \alpha_{\mathrm{2D}}^{\perp}/2\varepsilon_{0}$ (\AA{})\\
    \hline
    2H-MoS$_{2}$ & 40.0 & 2.50 \\
    2H-MoSe$_{2}$ & 45.5 & 2.72  \\
    2H-MoTe$_{2}$ & 58.1 & 3.07  \\
    2H-WS$_{2}$ & 35.7 & 2.46  \\
    2H-WSe$_{2}$ & 41.0 & 2.71 \\
    2H-WTe$_{2}$ & 53.5 &  3.17\\
    \hline
  \end{tabular}
\end{table}
